Trends of SDR in Thessaloniki

### 2023-06-28 Article.Rmd
Commit 2023-06-28 12:17

The shortwave downward solar irradiance (SDR) at the Earth's surface plays a significant role, on Earths climate.
Changes of the SDR can be related to major changes on the Earths energy budget, the climate change mechanisms and the water and carbon cycles [@Wild2009].
Studies of SDR variability, have identify some distinct SDR trends on different regions of the world and for different periods, using the term 'brightening' for positive trends, and 'dimming' for negative trends.

Multiple studies attempt to evaluate the phenomenon and the potential causes [@Ohvril2009; @Schwarz2020; @Wild2009; @Wild2012; @Xia2007; @Zerefos2009].
Although, there is regional variation of SDR, with both positive and negative trends, most of the studies agree that the major factors are the interaction of aerosols and clouds.

>>>>

The shortwave downward solar irradiance (SDR) at the Earth's surface plays a significant role, on Earths climate.
Changes of the SDR can be related to major changes on the Earths energy budget, the climate change mechanisms and the water and carbon cycles [@Wild2009].
Studies of SDR variability, have identify some distinct SDR trends on different regions of the world and for different time periods, using the term 'brightening' for positive trends, and 'dimming' for negative trends.
Multiple studies attempt to evaluate the phenomenon and the potential causes [@Ohvril2009; @Schwarz2020; @Wild2009; @Wild2012; @Xia2007; @Zerefos2009; and references therein].
There is a general consensus that the major factors of the attenuation of SDR is the interaction with the atmospheric aerosols and the clouds.

- observed long term changes
  europe / asia africa regions

Although, there is regional variation of SDR, with both positive and negative trends, most of the studies agree that .
